---
title: "Airbnb data"
author: "Davis Vaughan"
date: "1/20/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

http://tomslee.net/airbnb-data-collection-get-the-data


```{r}
library(tibbletime)
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(readr)
```

```{r}
airbnb <- read_csv("data/tomslee_airbnb_san_diego_1436_2017-07-11.csv") %>%
  as_tbl_time(last_modified) %>%
  arrange(last_modified) %>%
  select(last_modified, price, latitude, longitude)
```

# Slicing up your time series

- 5th hour of 2017-07-12
- Automatically coerced to the correct time zone and date object

```{r}
# All of 2017
# Not important but allows me to explain it
airbnb[~"2017"]

airbnb %>%
  filter(last_modified >= as.POSIXct("2017-07-12 02:00:00", tz = "UTC"), last_modified <= as.POSIXct("2017-07-12 02:59:59", tz = "UTC"))

airbnb %>%
  filter_time(~"2017-07-12 02")

airbnb[~"2017-07-12 02"]

# Start of 2nd hour to the end of the 3rd hour
airbnb %>%
  filter(last_modified >= as.POSIXct("2017-07-12 02:00:00", tz = "UTC"), last_modified < as.POSIXct("2017-07-12 03:59:59", tz = "UTC"))

airbnb %>%
  filter_time("2017-07-12 02" ~ "2017-07-12 03")
```

# A new way to group

Also the "extra functionality"

Showing different variations

```{r}
# First a simple collapse by 2 hour
airbnb %>%
  collapse_by(period = "1 sec")

# What can you do with this?
airbnb %>%
  collapse_by(period = "2 hour") %>%
  group_by(last_modified) %>%
  summarise(median_price = median(price))

# Clean up
airbnb %>%
  collapse_by(period = "2 hour", clean = TRUE) %>%
  group_by(last_modified) %>%
  summarise(median_price = median(price))

# Start
airbnb %>%
  collapse_by(period = "2 hour", clean = TRUE, side = "start") %>%
  group_by(last_modified) %>%
  summarise(median_price = median(price))

# This should go in the flexible section
airbnb %>%
  collapse_by(period = "2 hour", clean = TRUE, side = "start", start_date = "2017-07-11 15:00:00") %>%
  group_by(last_modified) %>%
  summarise(median_price = median(price))

boundaries <- as.POSIXct(x = c("2017-07-11 00:00:00", "2017-07-11 20:00:00"), tz = "UTC")

airbnb %>%
  collapse_by(period = boundaries, clean = TRUE, side = "start") %>%
  group_by(last_modified) %>%
  summarise(median_price = median(price))
```

```{r}
library(ggmap)
library(gganimate)

airbnb_plot <- airbnb %>%
  
  # Collapse and clean
  collapse_by(period = "hour", clean = TRUE, side = "start") %>%
  
  # Throw out a few outliers
  filter(between(price, quantile(price, .05), quantile(price, .95))) %>%
  
  # Map and animate
  qmplot(longitude, latitude, data = ., geom = "blank") +
  geom_point(aes(color = price, size = price, frame = last_modified), alpha = .5) +
  scale_color_continuous(low = "red", high = "blue")

animation::ani.options(ani.dev = "png", ani.type = "png", ani.width = 800, ani.height = 800, interval = 1.5)
gganimate(airbnb_plot, "test-example.gif")

```

# Let's get things rolling

Start off with an attention grabbing example. rollify()

Also lets me start with a stock example, and get it out of the way then
go back to airbnb which i will use for the rest of the time.

- rollify() is an adverb like what purrr has

```{r}
data(FB)

# Rolling averages

short_term_mean <- rollify(mean, window = 5)
long_term_mean  <- rollify(mean, window = 50)

FB_roll <- FB %>%
  mutate(short_mean = short_term_mean(adjusted),
         long_mean  = long_term_mean(adjusted)) 

FB_roll %>%
  select(date, adjusted, short_mean, long_mean)

FB_roll %>%
  tidyr::gather(key = "Indicator", value = "value", short_mean, long_mean, adjusted) %>%
  ggplot(aes(x = date, y = value, color = Indicator)) +
  geom_line() +
  labs(x = "Date", y = "Price", title = "FB Adjusted stock price with long/short term moving averages") +
  theme_minimal()
  
# Rolling regressions - more complex and arbitrary functions

lm_roll <- rollify(
  .f     = ~ lm(.y ~ .x), 
  window = 5, 
  unlist = FALSE
)


FB_model <- FB %>%
  mutate(
    lag_volume = lag(volume),
    model = lm_roll(lag_volume, adjusted)
  ) 

FB_model %>%
  select(date, adjusted, volume, lag_volume, model)

FB_model %>%
  filter(!is.na(model)) %>%
  mutate(glanced = map(model, broom::glance)) %>%
  select(date, glanced) %>%
  unnest()

```

