---
title: "Term Deposit Prediction & Marketing Analysis"
author: "Business Science"
date: "2/13/2019"
output:
  pdf_document: default
  html_document: default
subtitle: Targeting Customers that are likely to opt into a Term Deposit service
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE)
```

# Executive Summary

- Duration since last contact and success of prior enrollments are correlated to success of Term Deposit opt-in
- A strategy targeting customers that haven't been contacted in 319 days and have those with prior enrollments yields 32% positive outcomes (enrollments) vs 4.3% otherwise. 

# Analysis

```{r}
# Libraries
library(tidyverse)
library(readxl)
library(recipes)
library(tidyquant)
library(ggrepel)


# 1.0 READ EXCEL SHEETS ----
path   <- "data/bank_term_deposit_marketing_analysis.xlsx"
sheets <- excel_sheets(path)


# # 2.0 INVESTIGATE DATA FOR EACH SHEET ----
# sheets %>%
#     map(~ read_excel(path  = path, sheet = .)) %>%
#     set_names(sheets)


# 3.0 PERFORM VLOOKUP EQUIVALENT ----
data_joined_tbl <- sheets[4:7] %>%
    map(~ read_excel(path = path, sheet = .)) %>%
    reduce(left_join)

# 4.0 ANALYZE ----

# 4.1 Prepare Data ----
# recipes reference: https://tidymodels.github.io/recipes/reference/index.html

recipe_obj <- recipe(~ ., data = data_joined_tbl) %>%
    step_rm(ID) %>%
    step_discretize(all_numeric(), options = list(min_unique = 1)) %>%
    step_dummy(all_nominal(), one_hot = TRUE, naming = partial(dummy_names, sep = "__")) %>%
    prep()

data_transformed_tbl <- data_joined_tbl %>%
    bake(recipe_obj, new_data = .) 

# 4.2 Correlation Analysis ----

# Prepare Correlations
correlation_tbl <- data_transformed_tbl %>%
    cor(y = data_transformed_tbl$TERM_DEPOSIT__yes) %>%
    as_tibble(rownames = "feature") %>%
    rename(TERM_DEPOSIT__yes = V1) %>%
    separate(feature, into = c("feature", "bin"), sep = "__") %>%
    filter(!is.na(TERM_DEPOSIT__yes)) %>%
    filter(!str_detect(feature, "TERM_DEP")) %>%
    arrange(abs(TERM_DEPOSIT__yes) %>% desc()) %>%
    mutate(feature = as_factor(feature) %>% fct_rev())
```

Correlation of various features to Term Deposit enrollment. Duration since last contact and success of prior enrollments are correlated to success of Term Deposit opt-in.

```{r, fig.height=5}
# Visualize Correlations
correlation_tbl %>%
    
    ggplot(aes(TERM_DEPOSIT__yes, y = feature, text = bin)) +
    
    # Geometries
    geom_vline(xintercept = 0, linetype = 2, color = "red") +
    geom_point(color = "#2c3e50") +
    geom_text_repel(aes(label = bin), size = 3, color = "#2c3e50") +
    
    # Formatting
    expand_limits(x = c(-0.4, 0.4)) +
    theme_tq() +
    labs(title = "Bank Marketing Analysis",
         subtitle = "Correlations to Enrollment in Term Deposit",
         y = "", x = "Correlation to Term Deposit")
```

# Strategy

A strategy targeting customers that haven't been contacted in 319 days and have those with prior enrollments yields 32% positive outcomes (enrollments) vs 4.3% otherwise.

```{r}
strategy_tbl <- data_joined_tbl %>%
    select(DURATION, POUTCOME, TERM_DEPOSIT) %>%
    mutate(POTENTIAL = case_when(
        DURATION > 319 ~ "High Potential",
        POUTCOME == "success" ~ "High Potential",
        TRUE ~ "Normal"
    )) %>%
    group_by(POTENTIAL) %>%
    count(TERM_DEPOSIT) %>%
    mutate(prop = n / sum(n)) %>%
    ungroup() %>%
    mutate(label_text = str_glue("n: {n}
                                 prop: {scales::percent(prop)}"))

strategy_tbl %>%
    ggplot(aes(POTENTIAL, prop, fill = TERM_DEPOSIT)) + 
    geom_col() +
    geom_label(aes(label = label_text), fill = "white", color = "#2c3e50") +
    scale_fill_tq() +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_tq() +
    labs(title = "Bank Marketing Strategy",
         subtitle = str_glue("Targeting customers that haven't been contacted in 319 days 
                             or those with prior enrollments yields 32% vs 4.3%")
    )
```

