---
title: "Rstudio::conf 2018 walkthrough"
author: "Davis Vaughan"
date: "1/25/2018"
output: html_document
---

# Overview

This guide accompanies Davis Vaughan's rstudio::conf 2018 talk, 
"The future of time series and financial analysis in the tidyverse."

# Required packages

Unfortunately some of these packages are a bit finicky in what dependencies 
they require.

qqmap v2.6.1 (CRAN) requires ggplot2 v2.2.1 (CRAN) and will not work with the
dev version of ggplot2.

patchwork (Github only) requires and will automatically install the 
development version of ggplot2.

This causes problems if you want to run this code. I would advise running 
everything 1 chunk at a time with the CRAN version of ggplot2 until you get
down to the performance summary section. At that point, install patchwork with
`devtools::install_github("thomasp85/patchwork")` and run the rest of the
performance summary. 

```{r, message=FALSE}
# Business Science dev packages
# devtools::install_github("business-science/tibbletime")
# devtools::install_github("business-science/tidyquant2")
library(tibbletime)
library(tidyquant2)

# General packages
library(dplyr)
library(readr)
library(tidyr)

# Used for themes and getting data
library(tidyquant)

# For the mapping example
library(ggmap)
library(gganimate)

# For rolling linear models
library(broom)
```

# Tidyquant example

```{r}
tq_get("AAPL") %>%
  tq_mutate(select = adjusted, mutate_fun = dailyReturn) %>%
  ggplot(aes(x = date, y = daily.returns)) +
  geom_line() + 
  theme_tq()
```

# Airbnb data

```{r}
airbnb <- read_csv("../data/tomslee_airbnb_san_diego_1436_2017-07-11.csv") %>%
  as_tbl_time(last_modified) %>%
  arrange(last_modified) %>%
  select(last_modified, price, latitude, longitude)

airbnb
```

# Slicing up your time series

The dplyr way:

```{r}
airbnb %>%
  filter(
    last_modified >= as.POSIXct("2017-07-12 02:00:00", tz = "UTC"),     
    last_modified <= as.POSIXct("2017-07-12 02:59:59", tz = "UTC")
)
```

# tibbletime filter_time()

```{r}
airbnb %>%
  filter_time("2017-07-12 02:00:00" ~ "2017-07-12 02:59:59")

airbnb %>%
  filter_time(~"2017-07-12 02")
```

More examples

```{r}
# Filter for all days in 2017
airbnb %>%
  filter_time(~"2017")

# All days in July to the end of August
airbnb %>%
  filter_time("2017-07" ~ "2017-08")

# Start through the end of December
airbnb %>%
  filter_time("start" ~ "2017-12")
```

# A new way to group

```{r}
collapse_by(airbnb, period = "1 day")

collapse_by(airbnb, period = "1 day") %>% tail
```

Collapse and summarise

```{r}
# Collapse by 2 hour periods, summarise median price
airbnb %>%
  collapse_by(period = "2 hour") %>%
  group_by(last_modified) %>%
  summarise(median_price = median(price))

# Clean and round up
airbnb %>%
  collapse_by(period = "2 hour", clean = TRUE) %>%
  group_by(last_modified) %>%
  summarise(median_price = median(price))

# Clean and round down
airbnb %>%
  collapse_by(period = "2 hour", clean = TRUE, side = "start") %>%
  group_by(last_modified) %>%
  summarise(median_price = median(price))
```

# The possibilities are endless

This works with ggmap v2.6.1 (CRAN) and ggplot2 v2.2.1 (CRAN). It is a bit 
finicky with earlier version / dev versions of either package.

```{r}
airbnb_plot <- airbnb %>%
  
  # Collapse and clean
  collapse_by(period = "hour", clean = TRUE) %>%
  
  # Throw out a few outliers
  filter(
    between(price, quantile(price, .05), quantile(price, .95))
  ) %>%
  
  # Map and animate
  qmplot(longitude, latitude, data = ., geom = "blank") +
  geom_point(
    aes(color = price, size = price, frame = last_modified), 
    alpha = .5) +
  scale_color_continuous(low = "red", high = "blue")

gganimate(airbnb_plot)
```

# Let's get things rolling - rolling averages

```{r}
data(FB, package = "tibbletime")

short_term_mean <- rollify(mean, window = 5)
long_term_mean  <- rollify(mean, window = 50)

FB_roll <- FB %>%
  mutate(short_mean = short_term_mean(adjusted),
         long_mean  = long_term_mean(adjusted)) 

FB_roll %>%
  select(date, adjusted, short_mean, long_mean)
```

Moving average plot

```{r}
FB_roll %>%
  gather(key = "Indicator", value = "value", short_mean, long_mean, adjusted) %>%
  ggplot(aes(x = date, y = value, color = Indicator)) +
  geom_line() +
  labs(x = "Date", y = "Price", title = "FB Adjusted stock price with long/short term moving averages") +
  theme_minimal()
```

# Let's get things rolling - rolling linear models

```{r}
lm_roll <- rollify(
  .f     = ~ lm(.y ~ .x), 
  window = 5, unlist = FALSE)

FB_model <- FB %>%
  mutate(
    lag_volume = lag(volume),
    model = lm_roll(lag_volume, adjusted)
  ) 

FB_model
```

Looking at your model results with `broom`.

```{r}
FB_model %>%
  filter(!is.na(model)) %>%
  mutate(glanced = map(model, glance)) %>%
  select(date, glanced) %>%
  unnest()
```

# tidyfinance - FANG

```{r}
data(FANG, package = "tibbletime")

FANG_time <- FANG %>%
  group_by(symbol) %>% 
  as_tbl_time(date)

slice(FANG_time, 1:2)
```

```{r}
FANG_return <- FANG_time %>%
  select(symbol, date, adjusted) %>%
  calculate_return(adjusted, period = "daily") %>%
  mutate(drawdown = drawdown(adjusted_return),
         cum_ret  = cumulative_return(adjusted_return))

FANG_return
```

# tidyfinance + tibbletime

```{r}
FANG_return_monthly <- FANG_return %>%
  collapse_by("month") %>%
  group_by(symbol, date) %>%
  summarise(monthly_return = total_return(adjusted_return))

FANG_return_monthly
```

# Performance summary

Cumulative returns

```{r}
plot_cum_ret <- FANG_return %>%
  ggplot(aes(x = date, y = cum_ret, color = symbol)) +
  geom_line() +
  theme_tq() +
  theme(axis.title.x = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(
   y     = "Cumulative Return", 
   title = "Performance summary: Facebook, Amazon, Netflix, Google") +
  theme(legend.position="none") +
  scale_color_tq()
```

Monthly returns

```{r}
plot_month_ret <- FANG_return_monthly %>%
  ggplot(aes(x = date, y = monthly_return, fill = symbol)) +
  geom_col(width = 15, position = position_dodge()) +
  theme_tq() +
  theme(axis.title.x = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Monthly Return") +
  theme(legend.position="none") +
  scale_fill_tq()
```

Drawdown

```{r}
plot_drawdown <- FANG_return %>%
  ggplot(aes(x = date, y = drawdown, fill = symbol)) +
  geom_area(position = position_identity(), alpha = .7) +
  theme_tq() +
  scale_x_date(
    date_breaks = "3 months", 
    date_labels = "%b %Y") +
  labs(x = "", y = "Drawdown") +
  scale_fill_tq()
```

# Performance summary with patchwork

At this point you will need patchwork to run the following code, uncomment the
lines below to first install patchwork from github. It should also install 
the dev version of ggplot2. Then you will likely need to restart R and rerun 
the code that involves creating the 3 FANG charts that will be added together 
(everything _after_ the `tidyfinance - FANG` chunk along with loading
the required packages at the beginning).
Do not try and run the map code again, as it will not work now that you 
have the dev version of ggplot2.

```{r}
# For performance summary plots
devtools::install_github("thomasp85/patchwork", force = TRUE)
library(patchwork)

plot_cum_ret +
  plot_month_ret +
  plot_drawdown +
  plot_layout(ncol = 1, heights = c(2, 1, 1))
```


