---
title: "Tibbletime Demo"
author: "Matt Dancho"
date: "September 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = F,
    warning = F)
```

# What's It Used For?

1. The future of "tidy" time series analysis. New class `tbl_time` rests on top of `tbl` and makes tibbles time awaqe.

2. Can use a series of special tidy time series functions including `time_filter`, `time_summarize`, `as_period`, `time_collapse` and `tmap`. More coming!!!

# Load Libraries

```{r}
# devtools::install_github("business-science/tibbletime")
# devtools::install_github("business-science/tidyquant")
library(tibbletime) # Future of tidy time series analysis
library(tidyquant)  # Loads tidyverse, financial pkgs, used to get data
```

# Data

```{r}
# Stock Prices from Yahoo! Finance
FANG_symbols <- c("FB", "AMZN", "NFLX", "GOOG")

FANG_tbl_d <- FANG_symbols %>%
    tq_get(get = "stock.prices", from = "2014-01-01", to = "2016-12-31") 

FANG_tbl_d <- FANG_tbl_d %>%
    group_by(symbol)

FANG_tbl_d
```


Create a `tbl_time` object.

```{r}
# Convert to tbl_time
FANG_tbl_time_d <- FANG_tbl_d %>%
    as_tbl_time(index = date) 

FANG_tbl_time_d
```


# Special Time Series Functions

### time_filter

Succinctly filter a `tbl_time` object by date.

```{r}
# time_filter by day
FANG_tbl_time_d %>%
    time_filter(2014-06-01 ~ 2014-06-05)
```

```{r}
# time_filter by month
FANG_tbl_time_d %>%
    time_filter(2014-03 ~ 2014-12)
```

```{r}
# time filter combinations
FANG_tbl_time_d %>%
    time_filter(2014 ~ 2015-01-05) 
```

### time_summarize

Similar to `dplyr::summarise` but with the added benefit of being able to summarise by a time period such as "yearly" or "monthly"

```{r}
# Summarize functions over time periods such as weekly, monthly, etc
FANG_tbl_time_d %>%
    time_summarise(period = "yearly",
        adj_min   = min(adjusted),
        adj_max   = max(adjusted),
        adj_range = adj_max - adj_min
        )
```

### as_period

Convert a `tbl_time` object from daily to monthly, from minute data to hourly, and more. This allows the user to easily aggregate data to a less granular level.

```{r}
# Convert from daily to yearly periodicity
FANG_tbl_time_d %>%
    as_period(period = "yearly")
```

# Warning!

This package is currently under active development. Reproducible bug reports are welcome.

# More Information

* Check out our [GitHub Page](https://github.com/business-science/tibbletime)
* Check out our [Business Science Insights Blog](http://www.business-science.io/blog/index.html)