---
title: "Timetk Demo"
author: "Matt Dancho"
date: "September 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = F,
    warning = F)
```

# timetk: What's It Used For?

1. Coercing (converting) between time classes in R (e.g. between `tbl`, `xts`, `zoo`, `ts`)

2. Time series machine learning

# Load Libraries

```{r}
# devtools::install_github("business-science/timetk")
# devtools::install_github("business-science/tidyquant")
library(timetk)     # Functions working with time series
library(tidyquant)  # Loads tidyverse, financial pkgs, used to get data
```

# Data

Get data using `tidyquant`. The data comes from FRED: [Beer, Wine, and Distilled Alcoholic Beverages Sales](https://fred.stlouisfed.org/series/S4248SM144NCEN).

```{r}
# Beer, Wine, Distilled Alcoholic Beverages, in Millions USD
beer_sales_tbl <- tq_get("S4248SM144NCEN", get = "economic.data", from = "2010-01-01", to = "2016-12-31")

beer_sales_tbl
```

Visualize the data... nothing new here.

```{r}
# Plot Beer Sales
beer_sales_tbl %>%
    ggplot(aes(date, price)) +
    geom_line() +
    theme_tq() +
    labs(title = "Beer Sales")
```



# Part 1: Coercion

* __Problem__: Switching between various time classes in R is painful and inconsistent. 

* __Solution__: `tk_tbl`, `tk_xts`, `tk_zoo`, `tk_ts`

### tk_xts

Convert to `xts` using `tk_xts()`

```{r}
# xts
beer_sales_xts <- tk_xts(beer_sales_tbl) 

beer_sales_xts %>%
    head()
```

Can go from `xts` back to `tbl`.

```{r}
tk_tbl(beer_sales_xts, rename_index = "date")
```



### tk_ts

Convert to `ts` using `tk_ts()`.

```{r}
# ts
beer_sales_ts <- tk_ts(beer_sales_tbl, start = 2010, freq = 12)

beer_sales_ts
```

Can go back to `tbl`. Note that the date column is YEARMON class. 

```{r}
tk_tbl(beer_sales_ts, rename_index = "date")
```

Can go back to tibble and with `timetk_idx = TRUE` to __return original DATE or DATETIME information__.

```{r}
# Check for timetk index. 
has_timetk_idx(beer_sales_ts)
```

```{r}
# If timetk_idx is present, can get original dates back 
tk_tbl(beer_sales_ts, timetk_idx = TRUE, rename_index = "date")
```

# Part 2: Time Series Machine Learning

* __Key Insight__: The __time series signature__ - time stamp information expanded into a feature set - is used to perform machine learning.

* __Objective__: We'll predict the next 12 months of data for the time series. 

### Step 0: Review data

```{r}
# Starting point
beer_sales_tbl
```

### Step 1: Augment Time Series Signature

The `tk_augment_timeseries_signature()` function expands out the timestamp information into a machine learning feature set. Adds 28 columns of time series information. 

```{r}
# Augment (adds data frame columns)
beer_sales_tbl_aug <- beer_sales_tbl %>%
    tk_augment_timeseries_signature()

beer_sales_tbl_aug
```

### Step 2: Model

Apply any regression model to the data. We'll use `lm()`.

```{r}
# linear regression model used, but can use any model
fit_lm <- lm(price ~ ., data = select(beer_sales_tbl_aug, -c(date, diff)))

summary(fit_lm)
```

### Step 3: Build Future (New) Data

Use `tk_index()` to extract the index. 

```{r}
# Retrieves the timestamp information
beer_sales_idx <- beer_sales_tbl %>%
    tk_index()

tail(beer_sales_idx)
```

Make a future index from the existing index.

```{r}
# Make future index
future_idx <- beer_sales_idx %>%
    tk_make_future_timeseries(n_future = 12)

future_idx
```


From the future index, use `tk_get_timeseries_signature()` to turn index into time signature data frame.

```{r}
new_data_tbl <- future_idx %>%
    tk_get_timeseries_signature()

new_data_tbl
```


### Step 4: Predict the New Data

Use the `predict()` function for your regression model. 

```{r}
# Make predictions
pred <- predict(fit_lm, newdata = select(new_data_tbl, -c(index, diff)))

predictions_tbl <- tibble(
    date  = future_idx,
    value = pred
    )

predictions_tbl
```

Visualize our forecast. 

```{r}
# Plot Beer Sales Forecast
beer_sales_tbl %>%
    ggplot(aes(x = date, y = price)) +
    geom_line() +
    geom_line(aes(y = value), color = "blue", data = predictions_tbl) +
    theme_tq() +
    labs(title = "Beer Sales Forecast")
```

```{r}

```


# More Information

* Check out our [GitHub Page](https://github.com/business-science/timetk)
* Check out our [timetk documentation](https://business-science.github.io/timetk/)
* Check out our [Business Science Insights Blog](http://www.business-science.io/blog/index.html)