---
title: "Sweep Demo"
author: "Matt Dancho"
date: "September 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = F,
    warning = F)
```

# What's It Used For?

Tidying the `forecast` package workflow. Like `broom` is to `stats` library, `sweep` is to `forecast` package. 

# Load Libraries

```{r}
# devtools::install_github("business-science/sweep")
# devtools::install_github("business-science/timetk")
# devtools::install_github("business-science/tidyquant")
# install.packages("forecast")
library(sweep)      # Broom-style tidiers for the forecast package
library(timetk)     # Functions working with time series
library(tidyquant)  # Loads tidyverse, financial pkgs, used to get data
library(forecast)   # Forecasting models and predictions package
```

# Data

Get data using `tidyquant`. The data comes from FRED: [Panama Canal Traffic](https://fred.stlouisfed.org/series/S4248SM144NCEN).

```{r}
# Beer, Wine, Distilled Alcoholic Beverages, in Millions USD
panama_canal_tbl <- tq_get("M03028USM576NNBR", get = "economic.data", from = "1920-01-01", to = "1949-12-31")

panama_canal_tbl
```


Visualize the data... nothing new here.

```{r}
# Plot Panama Canal Traffic
panama_canal_tbl %>%
    ggplot(aes(date, price)) +
    geom_line() +
    theme_tq() +
    labs(title = "Panama Canal Traffic, Thousands of Tons")
```

# Forecasting using Forecast and Sweep

__Key Insight__:

Forecasting using the `forecast` package is a non-tidy process that involves `ts` class objects. We have seen this system before where we can "tidy" these objects. For the `stats` library, we have `broom`, which tidies models and predictions. For the `forecast` package we now have `sweep`, which tidies models and forecasts. 

__Objective__: We'll work through an ARIMA analysis to forecast the next 24 months of time series data. 

### Step 1: Create ts object

Use `timetk::tk_ts()` to convert from `tbl` to `ts`.

```{r}
# Convert from tbl to ts
panama_canal_ts <- tk_ts(panama_canal_tbl, start = 1920, freq = 12)

panama_canal_ts
```

### Step 2A: Model using ARIMA

We can use the `auto.arima()` function from the `forecast` package to model.

```{r}
# Model using auto.arima
fit_arima <- auto.arima(panama_canal_ts)

fit_arima
```


### Step 2B: Tidy the Model

Like `broom` tidies the `stats` package, we can use `sweep` functions to tidy the ARIMA model. 

```{r}
# sw_tidy - Get model coefficients
sw_tidy(fit_arima)
```

```{r}
# sw_glance - Get model and accuracy measures
sw_glance(fit_arima)
```

```{r}
# sw_augment - get model residuals
sw_augment(fit_arima, timetk_idx = TRUE)
```

Residual diagnostics.

```{r}
sw_augment(fit_arima, timetk_idx = TRUE) %>%
    ggplot(aes(x = index, y = .resid)) +
    geom_point() + 
    geom_hline(yintercept = 0, color = "red") + 
    labs(title = "Residual diagnostic") +
    theme_tq()
```



### Step 3: Make a Forecast

Make a forecast using the `forecast()` function. 

```{r}
# Forecast next 24 months
fcast_arima <- forecast(fit_arima, h = 24)
```

Use `sw_sweep()` to tidy the forecast output. 

```{r}
# sw_sweep - tidies forecast output
fcast_tbl <- fcast_arima %>%
    sw_sweep(timetk_idx = TRUE)

fcast_tbl
```

Visualize the forecast.

```{r}
# Visualize the forecast with ggplot
fcast_tbl %>%
    ggplot(aes(x = index, y = price, color = key)) +
    geom_ribbon(aes(ymin = lo.95, ymax = hi.95), 
                fill = "#D5DBFF", color = NA, size = 0) +
    geom_ribbon(aes(ymin = lo.80, ymax = hi.80, fill = key), 
                fill = "#596DD5", color = NA, size = 0, alpha = 0.8) +
    geom_line() +
    labs(title = "Panama Canal Traffic, ARIMA Forecast", x = "", y = "Thousands of Tons") +
    scale_x_date(date_breaks = "5 year", date_labels = "%Y") +
    scale_color_tq() +
    scale_fill_tq() +
    theme_tq()
```


# More Information

* Check out our [GitHub Page](https://github.com/business-science/sweep)
* Check out our [sweep vignettes](https://cran.r-project.org/web/packages/sweep/index.html)
* Check out our [Business Science Insights Blog](http://www.business-science.io/blog/index.html)