---
title: "Tidyquant Demo"
author: "Matt Dancho"
date: "September 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = F,
    warning = F)
```


# tidyquant: What's It Used For?

1. Getting web data from Yahoo! Finance, FRED Database, Quandl and more

2. Tidy application of financial and time series functions from `xts`, `zoo`, `quantmod`, `TTR` and `PerformanceAnalytics`

3. Graphing - Beautiful themes and financial geoms (e.g. `geom_ma`)

4. Working with portfolios

5. Financial performance analysis and portfolio attribution metrics

6. Great base for financial and time series analysis - Loads `tidyverse` and time series / financial packages behind the scenes making it a great starting point for any analysis

We'll go over first two in this tutorial. See documentation for other topics. 

# Load Libraries

```{r}
# devtools::install_github("business-science/tidyquant")
library(tidyquant) # Loads tidyverse, financial pkgs, used to get and manipulate data
```

# Getting data: tq_get

Use `tq_get()` to get data from the web. There's a bunch of API's it connects to including Yahoo! Finance, FRED Economic Database, Quandl, and more!

### Getting Stock Prices (Yahoo! Finance)

Pass a vector of stock prices to `tq_get()`.

```{r}
# Stock Prices from Yahoo! Finance
FANG_symbols <- c("FB", "AMZN", "NFLX", "GOOG")

FANG_data_d <- FANG_symbols %>%
    tq_get(get = "stock.prices", from = "2014-01-01", to = "2016-12-31")

FANG_data_d
```

### Getting Economic Data (FRED)

This example comes from __Deputy Chief Economist at Freddie Mac, Leonard Kieffer's__ recent article [A (TIDYQUANT)UM OF SOLACE](http://lenkiefer.com/2017/09/18/a-tidyquant-um-of-solace/)

Pass a vector of FRED symbols to `tq_get()`.

```{r}
# Economic Data from the FRED
FRED_symbols <- c('ETOTALUSQ176N',    # All housing units
                  'EVACANTUSQ176N',   # Vacant
                  'EYRVACUSQ176N',    # Year-round vacant
                  'ERENTUSQ176N'      # Vacant for rent
)

FRED_data_m <- FRED_symbols %>%
    tq_get(get="economic.data", from = "2001-04-01")

FRED_data_m
```

# Mutating Data: tq_transmute and tq_mutate

For applying `xts`, `zoo`, and `quantmod` functions in a "tidy" way. See below for [Available Functions](#available_functions). 


### tq_transmute

Returns a new data frame. Useful when __periodicity changes__ the number of rows in the data. 

```{r}
# Change periodicity from daily to monthly using to.period from xts
FANG_data_m <- FANG_data_d %>%
    group_by(symbol) %>%
    tq_transmute(
        select      = adjusted,
        mutate_fun  = to.period,
        period      = "months"
    )

FANG_data_m
```

Before transformation - Too much data.

```{r}
# Daily data
FANG_data_d %>%
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_point() +
    geom_line() +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    scale_color_tq() +
    theme_tq()
```

After transformation - Easy to understand.

```{r}
# Monthly data
FANG_data_m %>%
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_point() +
    geom_line() +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    scale_color_tq() +
    theme_tq()
```



### tq_mutate

Returns the original data plus the mutated data.

```{r}
# Lags - Get first 5 lags
column_names <- paste0("lag", 1:5)

FANG_data_d %>%
    select(symbol, date, adjusted) %>%
    group_by(symbol) %>%
    tq_mutate(
        select     = adjusted,
        mutate_fun = lag.xts,
        k          = 1:5,
        col_rename = column_names
    )
```

### Available Functions {#available_functions}

A bunch of functions that can be used!

```{r}
# Available functions
# mutate_fun =
tq_transmute_fun_options()
```

# More Information

* Check out our [GitHub Page](https://github.com/business-science/tidyquant)
* Check out our [tidyquant documentation](https://business-science.github.io/tidyquant/)
* Check out our [Business Science Insights Blog](http://www.business-science.io/blog/index.html)